%-------------------------
% Resume in Latex (Updated)
% Author : Aditya Maurya
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% Project title with external link icon
\newcommand{\projectLink}[3]{\href{#2}{\textbf{#1} \faExternalLink} $|$ \emph{#3}}

\begin{document}

%----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE Aditya Maurya} & \\
  NH-8, Bandar Sindri, Dist-Ajmer-305817, Rajasthan, INDIA & Mobile: +91-8079035137 \\
  \href{https://iditya.tech}{\underline{iditya.tech}} & \href{mailto:adiimaurya02@gmail.com}{\underline{adiimaurya02@gmail.com}} \\
  \href{https://linkedin.com/in/idityage}{\underline{linkedin.com/in/idityage}} & \href{https://github.com/idityaGE}{\underline{github.com/idityaGE}} \\
\end{tabular*}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading{Central University Of Rajasthan}{Ajmer, Rajasthan}{Bachelor of Technology in Computer Science and Engineering}{Aug. 2023 -- May 2027}
    \resumeItemListStart
      \resumeItem{\textbf{CGPA:} 8.66 (Till 3rd Sem)}
    \resumeItemListEnd
    \resumeSubheading{Chandra Public School}{Mau, Uttar Pradesh}{Senior Secondary (XII), Math and Science Stream}{2022}
    \resumeItemListStart
      \resumeItem{\textbf{Board:} CBSE \quad \textbf{Percentage:} 84.2\%}
    \resumeItemListEnd
    \resumeSubheading{Chandra Public School}{Mau, Uttar Pradesh}{Matriculation (X)}{2020}
    \resumeItemListStart
      \resumeItem{\textbf{Board:} CBSE \quad \textbf{Percentage:} 87.8\%}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading{Freelance Full-Stack Developer}{Remote}{Self-employed}{Jan 2025 -- Present}
    \resumeItem{\projectLink{Hyper Digital}{https://www.hyperdigital.in/}{Next.js, TypeScript, Cal.com, Nodemailer, Motion, Shadcn UI}}
    \resumeItemListStart
      \resumeItem{Designed and developed a fully responsive, SEO-friendly business website using Next.js and Shadcn UI.}
      \resumeItem{Enabled client onboarding via Cal.com integration and dynamic forms using TypeScript and Nodemailer.}
      \resumeItem{Collaborated with the agency to align branding, messaging, and layout with business goals.}
    \resumeItemListEnd
    \vspace{6pt}
    \resumeItem{\projectLink{BloomKnot}{https://bloomknot.in/}{Next.js, Cal.com, Better Auth, Nodemailer, Prisma, Postgres, Shadcn UI}}
    \resumeItemListStart
      \resumeItem{Built and deployed a modern web platform using Next.js and TypeScript with dynamic scheduling via Cal.com.}
      \resumeItem{Integrated Better Auth for secure authentication and used Nodemailer for transactional emails.}
      \resumeItem{Implemented admin-side tools for vendor coordination and logistics management.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading{\projectLink{Blind Chat}{https://blind-curaj.vercel.app/}{Next.js, TypeScript, Socket.io, Redis, Prisma, Postgres, Shadcn UI}}{}
    \resumeItemListStart
      \resumeItem{Built a real-time anonymous chat platform for college students using official email authentication.}
      \resumeItem{Implemented WebSocket-based real-time messaging with Socket.io and backend rate-limiting using Redis.}
      \resumeItem{Easily customizable via a simple config file to support any college's email.}
    \resumeItemListEnd
  \resumeProjectHeading{\projectLink{Zapier}{https://github.com/idityaGE/_zapier}{Kafka, Turborepo, Next.js, Zustand, TypeScript, Express, Prisma, Docker}}{}
    \resumeItemListStart
      \resumeItem{Created an open-source automation platform with a trigger-action framework similar to Zapier.}
      \resumeItem{Supports extensible app connectors and customizable workflows with reliable Kafka-based messaging.}
      \resumeItem{Modular architecture with Turborepo for scalable microservice development and deployment.}
    \resumeItemListEnd
  \resumeProjectHeading{\projectLink{Solana Token Launchpad}{https://solana-token-lauchpad.vercel.app/}{React, TypeScript, Solana Web3.js, SPL Token, Shadcn}}{}
    \resumeItemListStart
      \resumeItem{Developed a dApp to launch custom tokens on the Solana blockchain with full metadata support.}
      \resumeItem{Integrated Solana SPL Token and Anza Wallet Adapter for seamless user wallet interaction.}
      \resumeItem{Designed with Shadcn UI and TailwindCSS for a polished user experience.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: C/C++, Rust, Python, Java, TypeScript, Golang, Solidity, HTML/CSS, Bash} \\
    \textbf{Frameworks}{: React, Node.js, Next.js, Express, Hono.js, GraphQL, Web3.js} \\
    \textbf{Libraries}{: TailwindCSS, Zustand, Socket.io, TanStack Query, Turborepo, Motion, Vitest, Jest} \\
    \textbf{Database}{: PostgreSQL, MongoDB, Redis, MySQL} \\
    \textbf{Developer Tools}{: Git, GitHub, VS Code, Postman, Linux} \\
    \textbf{DevOps}{: AWS, Docker, Kubernetes, GitHub Actions, Apache Kafka, Cloudflare}
  }}
\end{itemize}

\end{document}
